---
title: "Project 1: Data Exploration and Visualization"
author: "Jenny Li, Xiang Li"
date: "2021/9/17"
output: html_document
---

---
title: "Project 1: Data Exploration and Visualization"
author: "INSERT YOUR NAME(S) HERE"
date: "Due Date Here"
output: html_document
---

<!--- Begin styling code. --->
<style type="text/css">
/* Whole document: */
body{
  font-family: "Palatino Linotype", "Book Antiqua", Palatino, serif;
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
<!--- End styling code. --->
```{r,message=FALSE,echo=FALSE}
library(tidyverse)
library(splitstackshape)
```


```{r,echo=FALSE,message=FALSE}
#  full_bg<-read_csv('https://raw.githubusercontent.com/bryandmartin/STAT155/master/docs/Projects/project1_bgdataviz/board_game_raw.csv')
#  
# write_csv(full_bg,"./Data/full_bg.csv")

full_bg<- read_csv("./Data/full_bg.csv")
```
#Instruction

#Mian Section

#Conclusion

# Code Appendix
```{r,eval=FALSE}
#all the code in here
```

