---
title: "Project 1: Data Exploration and Visualization"
author: "Jenny Li, Xiang Li"
date: "2021/9/17"
output: html_document
---

---
title: "Project 1: Data Exploration and Visualization"
author: "INSERT YOUR NAME(S) HERE"
date: "Due Date Here"
output: html_document
---

<!--- Begin styling code. --->
<style type="text/css">
/* Whole document: */
body{
  font-family: "Palatino Linotype", "Book Antiqua", Palatino, serif;
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
<!--- End styling code. --->
```{r,message=FALSE,echo=FALSE}
library(tidyverse)
library(splitstackshape)
```


```{r,echo=FALSE,message=FALSE}
# full_bg<-read_csv('https://raw.githubusercontent.com/bryandmartin/STAT155/master/docs/Projects/project1_bgdataviz/board_game_raw.csv')
#  
# write_csv(full_bg,"./Data/full_bg.csv")

full_bg<- read_csv("./Data/full_bg.csv")
```
#Instruction
I am only interested in games published in 1950 or later and with at least 25 ratings, so you will need to `filter()` the raw data. (Make sure never to save processed data over your original raw .csv file!)
* You may notice that `category` and `mechanic` variables are untidy. I recommend using the `cSplit()` function within the `splitstackshape` package to fix these. Try setting both `direction = "wide"` and `direction = "long"` within your `cSplit()` call. Both might be useful to you, depending on what plot you want generate.
* Your project should include at least 6 visualizations. Feel free to add more to tell a more complete and compelling story, but each visualization should contribute to the substance of your report.
* Your project should include at least 3 different types of visualizations (e.g. scatterplots, box plots, bar plots, histograms, line plots, etc.).
* Each visualization should include a caption that fully explains how to understand your visualization (i.e. explain all the components, legends, etc.). A good guideline is that someone who has not read your report should be able to look at just a visualization and its caption and fully understand what that visualization is showing.
* Each visualization, in order to contribute to your 6 visualization requirement, must be accompanied by at least one paragraph of text. This text should include an interpretation of your visualization as well as what is interesting about your visualization. A strong visualization will be accompanied by text explaining what patterns or insights it helps us glean from the data. Sometimes, you may find that you need two or more visualizations to make a single point. This is fine (and likely preferred if you think it's necessary), but it will only count towards 1 of your total visualizations.
* At the end of your report, you should include a code appendix with all of your code, from downloading the data to generating the figures. This code should be well-commented and follow the style guidelines we learned in class. Use comments to label which blocks of code correspond to which visualizations. *You should have no code in the main body of your report!* (Remember: you can use `echo = FALSE` to hide code.)

Keep in mind: **there are no right answers for this project!**
These are real data, and I'm hoping for creative and interesting analyses that tell a compelling story about the data rather than cookie cutter reports. Have some fun with it, and good luck!
```{r,echo=FALSE,message=FALSE}
full_bg%>%
  filter(yearpublished>=1950,users_rated>=25)

full_bgMechanic<-full_bg%>%
  cSplit("category", direction="wide")

full_bgCategory<-full_bg%>%
  cSplit("category", direction="long")
```


#Mian Section

#Conclusion

# Code Appendix
```{r,eval=FALSE}
#all the code in here
```

