---
title: "Project 1: Data Exploration and Visualization"
author: "Jenny Li, Xiang Li"
date: "2021/9/17"
output: html_document
---

<!--- Begin styling code. --->
<style type="text/css">
/* Whole document: */
body{
  font-family: "Palatino Linotype", "Book Antiqua", Palatino, serif;
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
<!--- End styling code. --->
```{r,message=FALSE,echo=FALSE}
library(tidyverse)
library(splitstackshape)
```


```{r,echo=FALSE,message=FALSE}
#full_bg<-read_csv('https://raw.githubusercontent.com/bryandmartin/STAT155/master/docs/Projects/project1_bgdataviz/boa#rd_game_raw.csv')
#write_csv(full_bg,"./Data/full_bg.csv")
full_bg<- read_csv("./Data/full_bg.csv")
```
#Instruction

```{r,echo=FALSE,message=FALSE,warning=FALSE}
#filter games published in 1950 or later and with at least 25 ratings
newFull_gb<-full_bg%>%
  filter(yearpublished>=1950,users_rated>=25)

full_gbMechanic<-newFull_gb%>%
  cSplit("category", direction="wide")

full_gbCategory<-newFull_gb%>%
  cSplit("category", direction="long")

full_gbMechanic2<-newFull_gb%>%
  cSplit("mechanic", direction="wide")

#searching for certain category(contains the word in the name)
catan<-newFull_gb%>%
  filter(grepl("Catan",name))
```


#Mian Section

>Visualtion one 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
#print(max(newFull_gb$yearpublished))

newFull_gb %>%
  ggplot(aes(x = yearpublished)) +
  labs(y = 'number of games published', x = 'years published') +
  #change the interval into 5 years each
  scale_x_continuous(breaks = seq(1950, 2020, by = 5)) +
  geom_histogram(binwidth = 5,color = "black",fill="deepskyblue4") +
  theme(plot.title = element_text (hjust = 0.5,
                                   face = "bold",
                                   size = 14)) +
  theme_minimal()

#median(newFull_gb$yearpublished)
```

This histogram shows the number of games published every five years from 1950-2020. As the graph shows, there are only a few games published in the 2015-2020 interval because the data is covered by 2018, so there is a lot of data missing in that interval. Other than that, the graph can be interpreted as left-skewed and has a long tail. The median of the graph might be around the year 2009. There is an instant increase appeared between 2000 and 2005, and 2005 and 2010, while following decades are also highly increased compared to the previous one. Thus, we assume from the graph that it will continuously increase in the following decades. 

One of our assumptions of such circumstances is that it might be associated with the fast development of technology development. There will be more producers coming into this market and publishing more and more games as the technology develops in the following decades.


>Visualization two 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
fac_lab = c(boardgame ="Board Game", boardgameexpansion="Board Game Expansion")

# filter the maxplaytime not equals to 0
newFull_gb0 <- newFull_gb %>%
  filter(maxplaytime != 0)

newFull_gb0 %>%
  ggplot(aes(x = maxplaytime)) +
  geom_histogram(binwidth = 20,  color = "black", fill = "aquamarine4", position = "identity") +
  theme_bw(base_size = 20) +
  labs(x = 'maximum playing time') +
  xlim(0, 400) +
  facet_grid(. ~ game_type, labeller = labeller(game_type = fac_lab))

# boardGame<-newFull_gb %>%
#   filter(game_type=='boardgame')
# 
# median(boardGame$maxplaytime)
# 
# boardGameExpansion<-newFull_gb %>%
#   filter(game_type=='boardgameexpansion')
# 
# median(boardGameExpansion$maxplaytime)

```

This multiple histogram graph shows how game type influences the maximum playing time of the games. Those graphs show that in the current existing games, board games are much more than the board game expansion and both types of the game contain the max playing time from 0 to 400 hours. Also, the maximum playing time of the board games concentrate around 45 whereas the board game expansion is relatively evenly distributed. In general, the board game expansion seems to have a relatively longer maximum playing time than the board game. Moreover, the existing games that contain very long maximum playing time in the board game could be considered as the outliers in the data set, whereas the board game expansion seems to be more concentrated and has fewer outliers.


>Visualization three 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# full_gbCategory %>%
#   count(game_type, category) %>%
#   group_by(category) %>%
#   mutate(relfreq = n / sum(n))

# full_gbCategory %>%
#   count(game_type, category) %>%
#   group_by(game_type) %>%
#   mutate(relfreq = n / sum(n))

category_choose <- full_gbCategory %>%
  filter(category %in% c("Card Game", "Expansion for Base-game", "Wargame", "Fantasy", "Fighting", "Science Fiction"))

category_choose %>%
  ggplot(aes(x = category, fill = game_type)) +
  geom_bar() +
  labs(x = 'categories of games', y = 'counts', fill = "type of game") +
  scale_fill_manual(values = c("steelblue", "lightblue"),
                    labels = c("Board Game", "Board Game Expansion")) +
  theme_bw(base_size = 11) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

```

This stacked bar plot compares two types of board games in the first six categories that contain the most games. Since the expansion for base-game and board game expansion are similar, the light blue which represents the board game expansion takes over the category of expansion for base-game. For the other categories, the number of board games is much more than the board game expansion in Card Games and War games, and the number of board games is also slightly more in fantasy, fighting, and science fiction. According to visualization 2, board games are much more than board game expansion, which correlates in visualization 3 that we can see board game outweighs board game expansion in most of the categories, except for Expansion for Base-game. 

We assume that maybe the game producers prefer to produce the board games since they might cost less or contain a higher profit. However, in some categories, the companies need to add new game areas, to create a better game experience, such as fantasy, fighting, and science fiction, which will be relatively evenly distributed into two types of game. In other categories of games, such as card games and war games, the necessity to combine with other elements is relatively low, with the number of board games being much more than the board game expansion.


>Visualization four 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
#count how may games in each category
categoryCounts<-full_gbCategory %>%
  count(category)
#resorted it in the decreasing number of games in each category
newOrderCa <- categoryCounts[order(-n)]
#filter the first six category to create a new dataset
firstSixCa<-
  full_gbCategory %>% filter(category == "Card Game"|category == "Expansion for Base-game"|category == "Wargame"|category == "Fantasy"|category == "Fantasy"|category == "Fighting"|category == "Science Fiction")
firstSixCa_rm0 <- firstSixCa %>%
  filter(average_complexity != 0)

#boxplot
firstSixCa_rm0 %>%
  ggplot(aes(x=category, y=average_complexity)) + # categorical on x, quantitative on y
  geom_boxplot(color = 'cadetblue4',fill="cadetblue2",alpha=1/5) +
  coord_flip() +
  labs(y = 'average complexity', x = 'categories of games') +
  theme_bw(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 40),
        axis.text = element_text(size=10),
        axis.text.x = element_text(hjust = 1, vjust = 1),
        axis.text.y = element_text(hjust = 1, vjust = 1))

```

These boxplots show the relationship between categories of the game and their average complexity. These boxplots are created based on the first six categories that contain most games. The one that contains most of the games (card game) lies at the bottom of the graph, and the others are arranged in decreasing order. As the graph shows, the median of the average complexity of card games is slightly lower than others which means that the card game might be a little easier than other types on average. It seems that the producer intentionally controls the average complexity of the games around 2 to 3, except for the card game which is around 1 to 2. Also, except for the expansion for base-game, which the higher average complexity it contains, the fewer games exist in that category. 

We assume that higher complexity games may use more resources to produce than low complexity games, which will lead to a relatively higher cost to produce higher complexity board games. Thus, we could assume that the higher the complexity, the fewer games would be produced, which might be associated with the higher cost and/or less demand for such games.


>Visualization five 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
newFull_gb1 <- newFull_gb %>%
  filter(average_complexity != 0)
newFull_gb1 %>%
  ggplot(aes(x = average_complexity , y = average_rating)) +
  geom_point(color = "steelblue", alpha = 0.2) +
  geom_smooth(method = 'lm',color='coral2')+
  labs(x = "average complexity", y = "average rating") +
  theme_bw(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 40),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(hjust = 1, vjust = 1),
        axis.text.y = element_text(hjust = 1, vjust = 1))
# cor(newFull_gb1$average_complexity, newFull_gb1$average_rating)
```

This scatterplot shows the relationship between the average rating and average complexity of these board games. They have a relatively moderate positive linear correlation (r = 0.5228426), but there are a few outliers. The average rating of the user towards the games is expected to find a positive difference in scores on average when comparing to the average complexity of the games that differs in scores by 1. When the average rating is between 5.0 and 7.5, more games are concentrating on average complexity between 1 and 4. When average complexity reaches 4 and 5, there are much fewer data points shown in the graph, inferring that there is much less rating for the games that have higher average complexity. So, we can also assume that there are fewer high complexity games.  

>Viualization six 

```{r,echo=FALSE,message=FALSE,warning=FALSE}
newFull_gb %>%
  ggplot(aes(x = users_rated, y = average_rating)) +
  labs(y = 'average rating', x = 'the number of users rated') +
  #take 5 points to complete a blue dot and add color to it
  geom_point(color = 'steelblue',alpha=1/5) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14)) +
  theme_minimal()
```

This scatterplot shows the relationship between the average rating and the number of users rated. Most users rated the game around the rating 7.5, which means the average rating and the number of users rated do not have a strong correlation. The rate of the games is mostly concentrated around 7.5, which indicates that the quality of the game is relatively even. There are more outliers around rating 7.5, and we can assume that more users rated the game, the game either be very popular, or it has been published for a very long time, or both.


>Conclusion

These visualization plots compare different variables in the dataset, build up some graphs that try to explain some of the relationship among the features among the board games.We used 5 different plots in these 6 visualizations to show the relationship between different variables. We can make assumptions of both users and producers based on these six visualizations.

Visualization 1 is a left-skewed histogram that shows the number of games published within every five years.

Visualization 2 is a side by side histogram which shows the two types of game versus their maximum playing time. Also, it shows that one type of game is much more than the other one while the other has a relatively longer max playing time on average.

Visualization 3 compares two types of board games in the first six categories that contain the most games by stacked bar plots. In general, the number of board games is more than the board game expansion, except the expansion for base-game.

Visualization 4 utilized boxplot to show the relationship between categories of the game and their average complexity. Resulting in the games have higher average complexity, the fewer games exist in that category, except for the expansion for base-game. 

Visualization 5 shows the relationship between the board games’ average rating and average complexity by using a scatter plot. They have a relatively moderate positive linear correlation, although there are a few outliers.

Visualization 6 shows the relationship between the average rating and the number of users rated by using a scatter plot. Resulting in a relatively weak relationship between the two variables.


# Code Appendix
```{r,eval=FALSE}
library(tidyverse)
library(splitstackshape)

#filter games published in 1950 or later and with at least 25 ratings
newFull_gb<-full_bg%>%
  filter(yearpublished>=1950,users_rated>=25)

full_gbMechanic<-newFull_gb%>%
  cSplit("category", direction="wide")

full_gbCategory<-newFull_gb%>%
  cSplit("category", direction="long")

full_gbMechanic2<-newFull_gb%>%
  cSplit("mechanic", direction="wide")

#searching for certain category(contains the word in the name)
catan<-newFull_gb%>%
  filter(grepl("Catan",name))

#Mian Section
#Visualization one
#print(max(newFull_gb$yearpublished))

newFull_gb %>%
  ggplot(aes(x = yearpublished)) +
  labs(y = 'number of games published', x = 'years published') +
  #change the interval into 5 years each
  scale_x_continuous(breaks = seq(1950, 2020, by = 5)) +
  geom_histogram(binwidth = 5,color = "black",fill="deepskyblue4") +
  theme(plot.title = element_text (hjust = 0.5,
                                   face = "bold",
                                   size = 14)) +
  theme_minimal()

#median(newFull_gb$yearpublished)

#Visualization Two
fac_lab = c(boardgame ="Board Game", boardgameexpansion="Board Game Expansion")

# filter the maxplaytime not equals to 0
newFull_gb0 <- newFull_gb %>%
  filter(maxplaytime != 0)

newFull_gb0 %>%
  ggplot(aes(x = maxplaytime)) +
  geom_histogram(binwidth = 20,  color = "black", fill = "aquamarine4", position = "identity") +
  theme_bw(base_size = 20) +
  labs(x = 'maximum playing time') +
  xlim(0, 400) +
  facet_grid(. ~ game_type, labeller = labeller(game_type = fac_lab))

# boardGame<-newFull_gb %>%
#   filter(game_type=='boardgame')
# 
# median(boardGame$maxplaytime)
# 
# boardGameExpansion<-newFull_gb %>%
#   filter(game_type=='boardgameexpansion')
# 
# median(boardGameExpansion$maxplaytime)

#Visualization Three
# full_gbCategory %>%
#   count(game_type, category) %>%
#   group_by(category) %>%
#   mutate(relfreq = n / sum(n))

# full_gbCategory %>%
#   count(game_type, category) %>%
#   group_by(game_type) %>%
#   mutate(relfreq = n / sum(n))

category_choose <- full_gbCategory %>%
  filter(category %in% c("Card Game", "Expansion for Base-game", "Wargame", "Fantasy", "Fighting", "Science Fiction"))

category_choose %>%
  ggplot(aes(x = category, fill = game_type)) +
  geom_bar() +
  labs(x = 'categories of games', y = 'counts', fill = "type of game") +
  scale_fill_manual(values = c("steelblue", "lightblue"),
                    labels = c("Board Game", "Board Game Expansion")) +
  theme_bw(base_size = 11) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

#Visualization Four
#count how may games in each category
categoryCounts<-full_gbCategory %>%
  count(category)
#resorted it in the decreasing number of games in each category
newOrderCa <- categoryCounts[order(-n)]
#filter the first six category to create a new dataset
firstSixCa<-
  full_gbCategory %>% filter(category == "Card Game"|category == "Expansion for Base-game"|category == "Wargame"|category == "Fantasy"|category == "Fantasy"|category == "Fighting"|category == "Science Fiction")
firstSixCa_rm0 <- firstSixCa %>%
  filter(average_complexity != 0)

#boxplot
firstSixCa_rm0 %>%
  ggplot(aes(x=category, y=average_complexity)) + # categorical on x, quantitative on y
  geom_boxplot(color = 'cadetblue4',fill="cadetblue2",alpha=1/5) +
  coord_flip() +
  labs(y = 'average complexity', x = 'categories of games') +
  theme_bw(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 40),
        axis.text = element_text(size=10),
        axis.text.x = element_text(hjust = 1, vjust = 1),
        axis.text.y = element_text(hjust = 1, vjust = 1))

#Visualization Five
newFull_gb1 <- newFull_gb %>%
  filter(average_complexity != 0)
newFull_gb1 %>%
  ggplot(aes(x = average_complexity , y = average_rating)) +
  geom_point(color = "steelblue", alpha = 0.2) +
  geom_smooth(method = 'lm',color='coral2')+
  labs(x = "average complexity", y = "average rating") +
  theme_bw(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 40),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(hjust = 1, vjust = 1),
        axis.text.y = element_text(hjust = 1, vjust = 1))
cor(newFull_gb1$average_complexity, newFull_gb1$average_rating)

#Visualization Six
newFull_gb %>%
  ggplot(aes(x = users_rated, y = average_rating)) +
  labs(y = 'average rating', x = 'the number of users rated') +
  #take 5 points to complete a blue dot and add color to it
  geom_point(color = 'steelblue',alpha=1/5) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 14)) +
  theme_minimal()
```
